%%% Please fill in basic information on your thesis, which will be automatically
%%% inserted at the right places. You need to replace \xxx{...} by real data.

% Type of your thesis:
%	"bc" for Bachelor's
%	"mgr" for Master's
%	"phd" for PhD
%	"rig" for rigorosum
\def\ThesisType{bc}

% Language of your study programme:
%	"cs" for Czech
%	"en" for English
\def\StudyLanguage{cs}

% Thesis title in English (exactly as in the formal assignment)
\def\ThesisTitle{Simulation and Reconstruction of~Charged Particle Trajectories in~an Aty\-pic Time Projection Chamber}

% Author of the thesis (you)
\def\ThesisAuthor{Martin Vavřík}

% Year when the thesis is submitted
\def\YearSubmitted{2025}

% Name of the department or institute, where the work was officially assigned
% (according to the Organizational Structure of MFF UK in English,
% see https://www.mff.cuni.cz/en/faculty/organizational-structure,
% or a full name of a department outside MFF)
\def\Department{Institute of Particle and Nuclear Physics}

% Is it a department (katedra), or an institute (ústav)?
\def\DeptType{Institute}

% Thesis supervisor: name, surname and titles
\def\Supervisor{Mgr. Tomáš Sýkora, Ph.D.}

% Supervisor's department (again according to Organizational structure of MFF)
\def\SupervisorsDepartment{Institute of Particle and Nuclear Physics}

% Study programme and specialization
\def\StudyProgramme{Physics}
%%% OLD??? \def\StudyBranch{Physics}

% An optional dedication: you can thank whomever you wish (your supervisor,
% consultant, a person who lent the software, etc.)
\def\Dedication{%
	I would like to thank my parents and my grandma for supporting me throughout my studies, and my supervisor Tomáš Sýkora and my consultant Hugo Natal da Luz for their encouragment, patience, and valuable insights.
}

% Abstract (recommended length around 80-200 words, try <= 120; this is not a copy of your thesis assignment!)
\def\Abstract{%
	In this work, we describe the development of a~reconstruction algorithm for atypical \acfp{TPC} that will be used at \acs{IEAPCTU} to search for the ATOMKI anomalous internal pair creation~\cite{atomki_be}. The chambers have an inhomogeneous toroidal magnetic field orthogonal to their electric field; hence we call them \acfp{OFTPC}. This arrangement causes a~distortion of the drift inside the chamber and complicates the shape of electron/positron trajectories. We present a~few approaches to tackle these problems, the best of which uses a~simulated ionization electron drift map for track reconstruction, and a~Runge-Kutta fit for energy reconstruction. Finally, we show from simulations that, for an ideal charge readout with no multiplication and no noise, and with exact knowledge of initial position and direction, we can reach \acs{FWHM} resolution of \qty{1.6}{\percent} for electrons and \qty{2.0}{\percent} for positrons without correcting systematic errors dependent on the track parameters. 
}

% 3 to 5 keywords (recommended) separated by \sep
% Keywords are useful for indexing and searching for the theses by topic.
\def\ThesisKeywords{%
	simulation \sep reconstruction \sep time projection chamber
}

% If any of your metadata strings contains TeX macros, you need to provide
% a plain-text version for use in XMP metadata embedded in the output PDF file.
% If you are not sure, check the generated thesis.xmpdata file.
\def\ThesisAuthorXMP{\ThesisAuthor}
\def\ThesisTitleXMP{\ThesisTitle}
\def\ThesisKeywordsXMP{\ThesisKeywords}
\def\AbstractXMP{In this work, we describe the development of a~reconstruction algorithm for atypical Time Projection Chambers (TPCs) that will be used at IEAP, CTU to search for the ATOMKI anomalous internal pair creation. The chambers have an inhomogeneous toroidal magnetic field orthogonal to their electric field; hence we call them Orthogonal Fields TPCs (OFTPCs). This arrangement causes a~distortion of the drift inside the chamber and complicates the shape of electron/positron trajectories. We present a~few approaches to tackle these problems, the best of which uses a~simulated ionization electron drift map for track reconstruction, and a~Runge-Kutta fit for energy reconstruction. Finally, we show from simulations that, for an ideal charge readout with no multiplication and no noise, and with exact knowledge of initial position and direction, we can reach FWHM resolution of 1.6~\% for electrons and 2.0~\% for positrons without correcting systematic errors dependent on the track parameters.}

% If your abstracts are long and do not fit in the infopage, you can make the
% fonts a bit smaller by this setting. (Also, you should try to compress your abstract more.)
\def\InfoPageFont{}
%\def\InfoPageFont{\small}  % uncomment to decrease font size

% If you are studing in a Czech programme, you also need to provide metadata in Czech:
% (in English programmes, this is not used anywhere)

\def\ThesisTitleCS{Simulace a~rekonstrukce drah nabitých částic v atypické časově projekční komoře}
\def\DepartmentCS{Ústav částicové a~jaderné fyziky}
\def\DeptTypeCS{Ústav}
\def\SupervisorsDepartmentCS{Ústav částicové a~jaderné fyziky}
\def\StudyProgrammeCS{Fyzika}

\def\ThesisKeywordsCS{%
    simulace \sep rekonstrukce \sep časová projekční komora
}

\def\AbstractCS{%
    V této práci byl vyvinut rekonstrukční algoritmus pro atypickou časovou projekční komoru (\acs{TPC}), jež bude použita na ÚTEF ČVUT k~hledání anomálie X17~\cite{atomki_be} ve vnitřní kreaci párů. Tyto komory mají nehomogenní toroidální magnetické pole, orientované kolmo k~elektrickému; proto je nazýváme TPC s~ortogonálními poli (\acs{OFTPC}). Toto uspořádání způsobuje distorzi driftu v~komoře a~komplikuje tvar elektronových a~pozitronových tracků. Představujeme několik řešení těchto komplikací, z~nichž nejlepší využívá simulaci mapy ionizačních elektronů pro rekonstrukci tracků a~Runge-Kutta fit pro rekonstrukci energie. Na závěr pomocí simulací demonstrujeme rozlišení (\acs{FWHM}) \qty{1.6}{\percent} pro elektrony a~\qty{2.0}{\percent} pro pozitrony, za předpokladu ideálního vyčítání náboje bez zesílení a~šumu, a~bez korekce systematických odchylek závislých na parametrech tracků.
}